Clean data

### 2020-09-02 analysis/02_clean-data.Rmd
Moved all of the data transformation into the data transformation block of 02_clean-data.Rmd

```{r shrink-data}
data <- data_clean %>% 
  mutate(id = row_number()) %>% 
  rename(version = vers_CBCONJOINT) %>% 
  select(id, version, Q1.1:Q5.18)
```

@@

@@

@@

>>>>

```{r shrink-data}
data <- data_clean %>% 
  mutate(id = row_number()) %>% 
  rename(version = vers_CBCONJOINT) %>% 
  select(-contains("_TEXT")) %>% 
  select(id, version, Q1.1:Q5.18)
```

@@

  ) %>% 
  mutate_at(
    # *Q2.3*: Which mediums do you use to follow news? (Select all that apply.)
    # - TV
    # - Print 
    # - Online (excluding social media) 
    # - Social media
    # - Radio
    # - Email newsletters
    # - News app
    vars(contains("Q2.3")), coalesce, 0
  ) %>%

@@

    # *Q5.10*: What is your current religion, if any?
    # - Catholic (including Roman Catholic and Orthodox)
    # - Protestant (United Church of Canada, Anglican, Orthodox, Baptist, Lutheran)
    # - Christian Orthodox
    # - Jewish
    # - Muslim
    # - Sikh
    # - Hindu
    # - Buddhist
    # - Atheist (do not believe in God)
    Q5.10 = factor(
      Q5.10, 
        "Catholic", "Protestant", "Christian Orthodox", "Jewish", 
        "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other"), 

@@

  ) %>% 
  mutate_at(
    # *Q5.16*: Choose one or more races that you consider yourself to be:
    # - White
    # - Black or African American
    # - American Indian or Alaska Native
    # - Asian
    # - Native Hawaiian or Pacific Islander
    vars(contains("Q5.16")), coalesce, 0
  ) %>% 
